\documentclass[a4paper,10pt]{cvclean}
\usepackage{xltxtra}
\usepackage{ulem}
\pagestyle{empty}

\name{J. Deon Garrett}
\position{Research Scientist in Artificial Intelligence and Assistant Professor of
  Computer Science}
\address{Stakkahlið 17, 105 Reykjavík, Iceland}
\home{+354.663.1594}
\email{deon@iiim.is}
\url{http://www.ru.is/starfsfolk/deong/}

\begin{document}
\setmainfont[Mapping=tex-text]{Cambria}
\makeheader


\begin{education}
\begin{degree}
    \type{Ph.D., Computer Science}
    \school{University of Memphis}
    \year{May, 2008}
    \thesis{Multiobjective Fitness Landscape Analysis and the Design of
      Effective Memetic Algorithms}
    \advisor{Dipankar Dasgupta}
\end{degree}
\begin{degree}
    \type{M.S., Computer Science}
    \school{Arkansas State University}
    \year{August, 1999}
    \thesis{Using Bidirectional Ray Tracing to Accurately Model Diffuse
      Lighting}
    \advisor{Edward T. Hammerand}
\end{degree}
\begin{degree}
    \type{B.S., Computer Science}
    \school{Arkansas State University}
    \year{May, 1998}
\end{degree}
\end{education}


\defsection{Research Interests}
\begin{Research Interests}
\begin{itemize}
\item Multiobjective and combinatorial optimization using metaheuristics. In
  particular, I am interested in understanding the structure of multiobjective
  search spaces and leveraging this information to construct better search and
  optimization algorithms for multiobjective problems.
\item Hyperheuristics -- algorithms that observe and react to perceived
  properties of a search space and adapt their behavior during the search
  accordingly.
\item Machine learning algorithms and applications.
\item Reinforcement learning.
\item Functional programming.
\end{itemize}
\end{Research Interests}


\begin{awards}
\begin{award}
  \title{Adaptive Resistance Control in Prosthetic Knee Joints}
  \role{\textbf{PI}}
  \duration{4 months}
  \amount{4.000.000 ISK}
  \collaborators{Össur, ehf. and Kristinn R. Thórisson, Reykjavík University}
  \startdate{May, 2014}
\end{award}
\begin{award}
  \title{Large Scale Machine Learning for Simultaneous Heterogeneous Tasks}
  \idnumber{EU Marie Curie CIG: 304210}
  \role{\textbf{PI}}
  \duration{3 years}
  \amount{€75,000}
  \collaborators{Kristinn Thórisson, Reykjavík University; Yngví Björnsson,
    Reykjavík University; Charles Anderson, Colorado State University}
  \startdate{May, 2012}
\end{award}
\end{awards}
  

\begin{publications}
  \begin{journalarticles}
    \begin{paper}
      \title{Optimal Wind Turbine Selection Methodology: A Case-Study for
        Búrfell, Iceland}
      \author{Samuel Perkin, \textbf{Deon Garrett}, and Pall Jensson}
      \journal{Renewable Energy}
      \misc{(Under review)}
      \month{August}
      \year{2014}
    \end{paper}
    \begin{paper}
      \title{Towards a General Attention Mechanism for Embedded Intelligent
        Systems}
      \author{Helgi Pall Helgason, Kristinn R. Thorisson, and \textbf{Deon
          Garrett}}
      \journal{International Journal of Computer Science and Artificial
        Intelligence}
      \vol{4}
      \num{1}
      \pages{1--7}
      \month{March}
      \year{2014}
    \end{paper}
    \begin{paper}
      \title{Comparison of Linear, Nonlinear, and Feature Selection Methods for
        EEG Signal Classification}
      \author{\textbf{Deon Garrett}, David Peterson, Charles Anderson, and Michael Thaut}
      \journal{IEEE Transactions on Neural Systems and Rehabilitation
        Engineering}
      \vol{11}
      \num{2}
      \pages{141--144}
      \month{June}
      \year{2003} 
      \misc{\textbf{Winner of the 2008 IEEE Engineering in Medicine and Biology Society
        (EMB) Award for Outstanding Paper in the Neural Systems technical area}}
    \end{paper}
  \end{journalarticles}

  \begin{bookchapters}
    \begin{paper}
      \title{Genetic-Based Solutions to Variations of the United States Navy's
        Sailor Assignment Problem}
      \author{Dipankar Dasgupta, \textbf{Deon Garrett}, German Hernandez, Fernando Nino,
        Andres Romero, Aishwarya Kaushal, and James Simien}
      \booktitle{Variants of Evolutionary Algorithms for Real-World Applications}
      \editor{Raymond Chiong, Thomas Weise, and Zbigniew Michalewicz}
      \publisher{Springer}
      \year{2011}
    \end{paper}
    \begin{paper}
      \title{Applying Multiobjective Evolutionary Algorithms to the Sailor
        Assignment Problem}
      \author{\textbf{Deon Garrett}, Dipankar Dasgupta, Joseph Vannucci, and James
        Simien}
      \booktitle{Advances in Evolutionary Computing for System Design}
      \editor{Lakhmi Jain, Vasile Palade, and Dipti Srinivasan}
      \publisher{Springer}
      \year{2007}
    \end{paper}
  \end{bookchapters}

  \begin{conferencepapers}
    \begin{paper}
      \title{Tunable and Generic Problem Instance Generation for Multi-task
        Reinforcement Learning}
      \author{\textbf{Deon Garrett}, Jordi Bieger, and Kristinn R. Thorisson}
      \conference{To appear in Proceedings of the IEEE Symposium on Adaptive Dynamic
        Programming and Reinforcement Learning (ADPRL '14)}
      \year{2014}
    \end{paper}
    \begin{paper}
      \title{Raising AI: Tutoring Matters}
      \author{Jordi Bieger, Kristinn R. Thórisson, and \textbf{Deon Garrett}}
      \conference{Artificial General Intelligence (AGI '14)}
      \venue{Montreal, Canada}
      \month{August}
      \year{2014}
    \end{paper}
    \begin{paper}
      \title{Wind Turbine Selection: A Case-Study for Búrfell Iceland}
      \author{Samuel Perkin, \textbf{Deon Garrett}, and Páll Jensson}
      \conference{Submitted to the 2014 Genetic and Evolutionary Computation
        Conference (GECCO '14)}
      \year{2014}
    \end{paper}
    \begin{paper}
      \title{A Call for Collaborative Landscape Analysis}
      \author{\textbf{Deon Garrett}}
      \conference{First Workshop on Understanding Problems: (GECCO '12)}
      \venue{Philadelphia, PA}
      \month{July}
      \year{2012}
    \end{paper}
    \begin{paper}
      \title{PMF: A Multicore-Enabled Framework for the Construction of
        Metaheuristics for Single and Multiobjective Optimization}
      \author{\textbf{Deon Garrett}}
      \conference{Parallel Problem Solving From Nature (PPSN '10)}
      \venue{Krakow, Poland}
      \month{September}
      \year{2010}
    \end{paper}
    \begin{paper}
      \title{A Conceptual Model of Self-Monitoring Multi-Core Systems}
      \author{Dipankar Dasgupta, Harkeerat Bedi, and \textbf{Deon Garrett}}
      \conference{Sixth Annual Workshop on Cyber Security and Information
        Intelligence Research (CSIIRW)}
      \venue{Oak Ridge, TN}
      \month{April}
      \year{2010}
    \end{paper}
    \begin{paper}
      \title{A Multiobjective Evolutionary Algorithm for the Task-Based Sailor
        Assignment Problem}
      \author{Dipankar Dasgupta, Fernando Nino, \textbf{Deon Garrett}, Koyel Chaudhuri,
        Soujanya Medapati, Aishwarya Kaushal, and James Simien}
      \conference{Genetic and Evolutionary Computation Conference (GECCO '09)}
      \venue{Montreal, Canada}
      \month{July}
      \year{2009}
    \end{paper}
    \begin{paper}
      \title{Plateau Connection Structure and Multiobjective Metaheuristic
        Performance}
      \author{\textbf{Deon Garrett}}
      \conference{IEEE Congress on Evolutionary Computation (CEC '09)}
      \venue{Trondheim, Norway}
      \month{May}
      \year{2009}
    \end{paper}
    \begin{paper}
      \title{An Empirical Comparison of Memetic Algorithm Strategies on the
        Multiobjective Quadratic Assignment Problem}
      \author{\textbf{Deon Garrett} and Dipankar Dasgupta}
      \conference{IEEE Symposium on Computational Intelligence}
      \venue{Nashville, TN}
      \month{March}
      \year{2009}
    \end{paper}
    \begin{paper}
      \title{On The Use of Informed Initialization and Extreme Solutions
        Sub-population in Multiobjective Evolutionary Algorithms}
      \author{Dipankar Dasgupta, German Hernandez, Andres Romero, \textbf{Deon Garrett},
        Aishwarya Kaushal, and James Simien}
      \conference{IEEE Symposium on Computational Intelligence}
      \venue{Nashville, TN}
      \month{March}
      \year{2009}
    \end{paper}
    \begin{paper}
      \title{User Identification Using GUI Manipulation Patterns and Artificial
        Neural Networks}
      \author{Eric S. Imsand, \textbf{Deon Garrett}, and John A. Hamilton Jr.}
      \conference{IEEE Symposium on Computational Intelligence}
      \venue{Nashville, TN}
      \month{March}
      \year{2009}
    \end{paper}
    \begin{paper}
      \title{A Comparison of Multiobjective Evolutionary Algorithms with
        Informed Initialization and the Kuhn-Munkres Algorithm for the Sailor
        Assignment Problem} 
      \author{Dipankar Dasgupta, German Hernandez, \textbf{Deon Garrett}, Pavan
        K. Vejandla, Aishwarya Kaushal, Ramjee Yerneni, and James Simien}
      \conference{Genetic and Evolutionary Computation Conference (GECCO '08)}
      \venue{Atlanta, GA}
      \month{July}
      \year{2008}
    \end{paper}
    \begin{paper}
      \title{Multiobjective Landscape Analysis and the Generalized Assignment
        Problem}
      \author{\textbf{Deon Garrett} and Dipankar Dasgupta}
      \conference{Learning in Intelligent Optimization (LION-II)}
      \venue{Trento, Italy}
      \month{December}
      \year{2007}
    \end{paper}
    \begin{paper}
      \title{A Framework for Evolving Multi-Shaped Detectors in Negative Selection}
      \author{Sankalp Balachandran, Dipankar Dasgupta, Fernando Nino, and \textbf{Deon
        Garrett}}
      \conference{IEEE Symposium on Foundations of Computational Intelligence
        (FOCI '07)}
      \venue{Honolulu, HI}
      \month{April}
      \year{2007}
    \end{paper}
    \begin{paper}
      \title{Analyzing the Performance of Hybrid Evolutionary Algorithms for the
        Multiobjective Quadratic Assignment Problem}
      \author{\textbf{Deon Garrett} and Dipankar Dasgupta}
      \conference{IEEE Congress on Evolutionary Computation (CEC '06)}
      \venue{Vancouver, Canada}
      \month{July}
      \year{2006}
    \end{paper}
    \begin{paper}
      \title{Genetic Algorithms for the Sailor Assignment Problem}
      \author{\textbf{Deon Garrett}, Dipankar Dasgupta, Rodrigo Silva, Joseph Vannucci,
        and James Simien}
      \conference{Genetic and Evolutionary Computation Conference (GECCO '05)}
      \pages{1921--1928}
      \venue{Washington, DC}
      \month{July}
      \year{2005}
      \misc{\textbf{Nominated for Best Paper award in Real World Applications track.}}
    \end{paper}
    \begin{paper}
      \title{Quad Search and Hybrid Genetic Algorithms}
      \author{Darrell Whitley, \textbf{Deon Garrett}, and Jean-Paul Watson}
      \conference{Genetic and Evolutionary Computation Conference (GECCO '03)}
      \pages{1469--1480}
      \venue{Chicago, IL}
      \month{July}
      \year{2003}
    \end{paper}
  \end{conferencepapers}

  \begin{presentations}
    \begin{talk}
      \title{Pareto Connection Graphs and Metaheuristic Performance}
      \author{\textbf{Deon Garrett}}
      \conference{INFORMS Annual Meeting}
      \venue{Washington, DC}
      \month{October}
      \year{2008}
    \end{talk}  
    \begin{talk}
      \title{GenoSAP-II Final Report}
      \author{\textbf{Deon Garrett}, Dipankar Dasgupta, German Hernandez}
      \conference{Navy Personnel Research, Studies, and Technology}
      \venue{Millington, TN}
      \month{August}
      \year{2008}
    \end{talk}
    \begin{talk}
      \title{How To \sout{Write Your} Type My Dissertation: Optimizing Keyboard Layout for \LaTeX\ 
        and C++}
      \author{\textbf{Deon Garrett}}
      \conference{Student Research Forum}
      \venue{Memphis, TN}
      \month{April}
      \year{2008}
      \misc{$\mathbf{1^{st}}$ \textbf{Runner Up for Best Presentation}}
    \end{talk}
    \begin{talk}
      \title{GenoSAP Final Report}
      \author{\textbf{Deon Garrett}, Dipankar Dasgupta, Joseph Vannucci, Rodrigo Silva}
      \conference{Navy Personnel Research, Studies, and Technology}
      \venue{Millington, TN}
      \month{August}
      \year{2005}
    \end{talk}
  \end{presentations}
\end{publications}


\begin{experience}{Research Experience}
\begin{job}
    \employer{Icelandic Institute for Intelligent Machines}
    \position{Research Scientist}
    \description{Perform research into machine learning and other aspects of
      Artificial General Intelligence. Responsible for supervision of projects,
      grant proposals, as well as coding and algorithm design issues.}
    \when{August, 2010 -- Present}
\end{job}
\begin{job}
    \employer{University of Memphis}
    \position{Postdoctoral Research Associate}
    \description{Supervised a team of graduate students on an incremental grant
      from Navy Personnel Research, Studies, and Technology (NPRST) working on a
      multiobjective combinatorial optimization problem optimizing the
      scheduling and assignment of sailors to available jobs and continued
      participation in weekly research group meetings.  Position held
      concurrently with position at AutoZone, Inc.}
    \when{March, 2008 -- May, 2010}
\end{job}
\begin{job}
    \employer{University of Memphis}
    \position{Graduate Research Assistant}
    \description{Worked on a grant funded by the United States Navy Personnel
      Research, Studies, and Technology.  The work led to the development of
      evolutionary and other metaheuristics aimed at the problem of optimally
      assigning sailors to available jobs.  Participated in weekly research
      group meetings as part of the Intelligent Security Systems Research
      Laboratory under Professor Dipankar Dasgupta.  Research topics and
      presentations included evolutionary computation, local search, landscape
      analysis, support vector machines, and applications to computer
      security and other areas.}
    \when{August, 2004 -- March, 2008}
\end{job}
\begin{job}
    \employer{Colorado State University}
    \position{Graduate Research Assistant}
    \description{Performed research in artificial intelligence, primarily in the
      areas of genetic algorithms, local search, and machine learning
      algorithms.  Problem domains included computer security and intrusion
      detection, EEG pattern recognition, and weather prediction from
      atmospheric satellite data.}  
    \when{June, 2000 -- December, 2002}
\end{job}
\end{experience}

\begin{experience}{Teaching Experience}
\begin{job}
    \employer{Reykjavík University}
    \position{Assistant Professor, School of Computer Science}
    \description{Joint appointment with IIIM, involves light teaching and
      service responsibilities.}
    \when{April, 2011 -- Present}
\end{job}
\begin{job}
    \employer{University of Memphis}
    \position{Graduate Teaching Assistant}
    \description{Taught courses in the Department of Computer Science
      including Introduction to Java Programming, Data Structures, and
      a laboratory for Discrete Mathematics.}
    \when{August, 2004 -- July, 2006}
\end{job}
\begin{job}
    \employer{Arkansas State University}
    \position{Visiting Instructor in Computer Science}
    \description{Taught numerous courses in Computer Science, including
      Programming I, Programming II, Computer Architecture, Operating Systems,
      Software Engineering I, and Software Engineering II.}
    \when{August, 2003 -- May, 2004}
\end{job}
\begin{job}
    \employer{Colorado State University}
    \position{Graduate Teaching Assistant}
    \description{Aiding in the teaching and administration of a course in
      Artificial Intelligence under Professor Adele Howe.  Responsibilities included
      occasional lectures, maintaining the course web site, grading assignments,
      and assisting students during office and lab hours.  Nominated by the
      students for the departmental award for outstanding teaching assistant by
      the students.}
    \when{August, 2002 -- December, 2002}
\end{job}
\begin{job}
    \employer{Lyon College}
    \position{Visiting Instructor in Computer Science}
    \description{Taught courses in Computer Science and Mathematics.
    Assisted in development of the Computer Science major.  Courses
    taught include C/C++ Programming, Data Structures, Analysis of
    Algorithms, Discrete Mathematics, Assembly Language and Computer
    Organization, and Elementary Functions.}
\when{August, 1999 -- May, 2000}
\end{job}
\begin{job}
    \employer{Arkansas State University}
    \position{Graduate Teaching Assistant}
    \description{Taught several developmental mathematics courses and
                performed other miscellaneous departmental duties.}
    \when{May, 1998 -- July, 1999}
\end{job}
\end{experience}


\begin{experience}{Professional Experience}
\begin{job}
    \employer{Greind Technologies, LLC}
    \position{Founder and Director}
    \description{Consulting firm specializing in contract software development,
      particularly in mobile application development. Current sales to date
      exceeding \$60,000 US.}
    \when{June, 2012 -- Present}
\end{job}
\begin{job}
    \employer{AutoZone, Inc.}
    \position{Technical Architect, R\&D}
    \description{Led R\&D initiatives to implement and deploy numerous projects,
      including a complete ``Buy Online, Pick up in Store'' solution and a
      unified search engine for many previously isolated AutoZone information
      repositories. Ongoing work includes development of mobile solutions based
      on the iPhone for both customers and internal personnel and providing
      expertise in rewriting a large C++ application currently suffering from
      significant problems.}
    \when{January, 2009 -- August, 2010}
\end{job}
\begin{job}
    \employer{AutoZone, Inc.}
    \position{Sr. Programmer Analyst, R\&D}
    \description{Investigated and developed hardware and software solutions for
      various requirements throughout the organization, including self-checkout
      kiosks, GPS tracking of commercial delivery vehicles, and a move to
      graphical software development using the Qt framework. I served as a
      primary liason between the R\&D group and the AutoZone software
      engineering and project management structure.}
    \when{June, 2007 -- January, 2009}
\end{job}
\begin{job}
    \employer{AutoZone, Inc.}
    \position{Programmer Analyst}
    \description{Worked on the development and deployment of AutoZone's next
      generation part lookup application, Z-net.  After previous attempts at
      constructing Z-net had been delayed by two years, my team delivered the
      application on time. In addition to design and coding, I handled the
      preparation and execution of released versions of the software to the more
      than 4000 stores in the AutoZone chain.}
    \when{January, 2007 -- June, 2007}
\end{job}
\begin{job}
    \employer{AutoZone, Inc.}
    \position{Programmer}
    \description{Supported numerous in-house C and C++ applications and assisted
      in the development of AutoZone's next generation part lookup application,
      Z-net.}
    \when{August, 2006 -- January, 2007}
\end{job}
\end{experience}


\defsection{Professional Activities}
\begin{Professional Activities}
\begin{itemize}
\item International Conference on Artificial Intelligence and Statistics
  (AISTATS 2014) (Local chair)
\item European Machine Learning Summer School (MLSS-Iceland 2014) (Local chair)
\item Genetic and Evolutionary Computation Conference (GECCO) (Program Committee
  (PC)).
\item Learning in Intelligent Optimization (LION) (PC).
\item IEEE Transactions on Evolutionary Computation (Referee).
\item IEEE Congress on Evolutionary Computation (CEC) (PC).
\item Evolutionary Computation (Referee).
\item European Conference on Artificial Intelligence (ECAI) (PC).
\item European Conference on Machine Learning (ECML-PKDD) (PC).
\item Workshop on Understanding Problems at GECCO 2012 (Referee).
\item Artificial General Intelligence (AGI) (PC).
\item Workshop on Self-Programming in AGI Systems, part of Artificial
  General Intelligence (AGI '11) (Organizer).
\item Natural Computing (Referee).
\item Engineering Applications of Artificial Intelligence (Referee).
\item Journal of Neuroscience Methods (Referee).
\item Biomedical Signal Processing and Control (Referee).
\item Computer Methods and Programs in Biomedicine (Referee).
\item Annual Simulation Symposium (ANSS '09), Part of the 2009 ACM Spring
  Simulation Multiconference (Referee).
\end{itemize}
\end{Professional Activities}


\defsection{Technical Skills}
\begin{Technical Skills}
\begin{itemize} 
\item C/C++
\item Python
\item Unix (Systems Programming, POSIX utilities, etc.)
\item Clojure
\item Java
\item Common Lisp
\item Haskell
\item MATLAB
\item Proficiency in many others
\end{itemize}
\end{Technical Skills}


\defsection{Courses Taught}
\begin{Courses Taught}
\begin{itemize}
\item Programming I (C++, Java) (UG; Arkansas State University, Lyon College,
  University of Memphis)
\item Programming II (C++, Java) (UG; ASU, UM)
\item Data Structures (UG; UM, LC)
\item Elementary Functions (UG; LC)
\item Laboratory for Discrete Mathematics (UG; UM)
\item Operating Systems (UG; ASU)
\item Computer Architecture (UG; ASU)
\item Assembly Language Programming (UG; LC)
\item Advanced Data Structures and Analysis of Algorithms (UG; LC)
\item Software Engineering I (UG/G; ASU)
\item Software Engineering II (UG/G; ASU)
\item Introduction to Machine Learning (UG/G; RU)
\item Advanced Topics in Machine Learning (G; RU)
\item Guest lectures in graduate research seminars in Computational Intelligence
  and Artificial Intelligence
\end{itemize}
\end{Courses Taught}

\defsection{Professional Societies}
\begin{Professional Societies}
\begin{itemize}
\item ACM
\item SIGEVO (ACM Special Interest Group on Evolutionary Computation)
\item AAAI
\item INFORMS
\end{itemize}
\end{Professional Societies}

\end{document}
